\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-06-22 Manuscript/Lanuza_et_al_2021.Rmd
edits on manuscript

```{=tex}
\doublespacing
\normalsize
```
\textbf{Statement of authorship:} JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.

\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.

\textbf{Short title:} Covariation among plant reproductive traits.

\textbf{Keywords:} life-history strategies \| plant reproductive traits \| plant-pollinator interactions.

\textbf{Type of article:} Letter.

\textbf{Number of words:} Abstract (146 words), main text excluding references, acknowledgements and captions (4983 words).

\textbf{Number of references:} 75

\textbf{Number of figures and tables:} 4 figures and 1 table.

@@

\newpage

@@

**Authors’contributions.**

@@

\clearpage

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies. The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation. The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation. The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}

@@

>>>>

```{=tex}
\doublespacing
\normalsize
```

@@

@@

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="95%", fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Figure 1} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies. The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation. The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation. The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}

@@

**Authors’contributions.** JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.

### 2022-06-22 Manuscript/Lanuza_et_al_2021.tex
edits on manuscript

\textbf{Statement of authorship:} JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.

\textbf{Data accessibility statement:} All data and code used to conduct this study will be deposited in the public repository Dryad upon acceptance.

\textbf{Short title:} Covariation among plant reproductive traits.

\textbf{Keywords:} life-history strategies \textbar{} plant reproductive traits \textbar{} plant-pollinator interactions.

\textbf{Type of article:} Letter.

\textbf{Number of words:} Abstract (146 words), main text excluding references, acknowledgements and captions (4983 words).

\textbf{Number of references:} 75

\textbf{Number of figures and tables:} 4 figures and 1 table.

@@

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2). We thank all researchers that made their data openly available and sent it upon request. We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection. We also thank Jason Tylianakis for his comments on the manuscript before submission. Finally, JBL thanks the University of New England for the funding provided to carry out this work.

\clearpage

{\centering \includegraphics{output/figures/unnamed-chunk-2-1}

>>>>

@@

{\centering \includegraphics[width=0.95\linewidth]{output/figures/unnamed-chunk-2-1}

@@

\textbf{Data accessibility.} All data and code used to conduct this study will is deposited at Zenodo

\textbf{Authors'contributions.} JBL, RR and IB designed the study. JBL collated the data and conducted analysis with guidance of JS, LKK and IB. JBL wrote the manuscript with contributions of all authors.

\textbf{Conflict of interest declaration.} We declare we have no competing interests.

\textbf{Funding.} This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).

\textbf{Acknowledgements.} We thank all researchers that made their data openly available and sent it upon request. We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection. We also thank Jason Tylianakis for his comments on the manuscript before submission. Finally, JBL thanks the University of New England for the funding provided to carry out this work.
